CODECHECK: An open-science initiative to facilitate sharing of computer programs and results presented in scientific publications.

### 2020-09-17 codecheck-paper.tex
ship out ...

@@

What can you expect to find a certificate? Draw an annotated example.

Should we annotate a certificate, at least the cover page, to
demonstrate what we mean by a certificate? We could print a four page
certificate 4-up so that it fits onto one page. Text might be too small
though to read? A 2-up, printed sideways would work well though.

>>>>

\usepackage{booktabs}

@@

What can you expect to find in  a CODECHECK certificate? Draw an annotated example.

\begin{table}
  \centering

  \begin{tabular}{lllp{9cm}}  \toprule
    Certificate & Ref & Research area & Description \\ \midrule
    2020-001 & \cite{cert-2020-001} & Machine learning & CODECHECK undertaken post acceptance of manuscript and before its publication in \textit{Gigascience} \cite{Piccolo2020-lo}.
    \\ 
    2020-002 & \cite{cert-2020-002} & neuroscience &
    Paper from 1997 showing unsupervised learning on images \cite{Hancock1992-mp} \\
    2020-003 & \cite{cert-2020-003} & neuroscience &
    Classic paper from 1982 on  models of associative memory \cite{Hopfield1982-mz} \\
    2020-004 & \cite{cert-2020-004} & area & barto \\
    2020-005 & \cite{cert-2020-005} & area & Larisch \\
    2020-006 & \cite{cert-2020-006} & area & Detorakis \\
    2020-007 & \cite{cert-2020-007} & area & in progress \\
    2020-008 & \cite{cert-2020-008} & Covid & covid-uk Davies \\
    2020-009 & \cite{cert-2020-009} & Covid &  tracing \\
    2020-010 & \cite{cert-2020-010} & Covid &  report 9 \\
    2020-011 & \cite{cert-2020-011} & Covid &  nature europe \\
    \\ \bottomrule
  \end{tabular}
  \caption{Register of completed certificates.  An interactive version
  of this is available at \url{http://codecheck.org.uk/register}.}
  \label{tab:register}
\end{table}

As an example, we have taken the certificate 2020-012
\cite{cert-2020-012}, and shown the first four pages (the remaining N
pages contain other example outputs), see Figure~\ref{fig:cert}.  This
certificate corresponded to a preprint on the modelling of COVID-19 in
the USA.i
%% TODO - has this been published yet?.
Figure~\ref{fig:cert} shows an annotation of the first four (out of
ten) pages for the certificate for this codecheck.
Figure~\ref{fig:cert}A shows the certificate number, and its DOI,
which points to the certificate as archived on Zenodo.
Figure~\ref{fig:cert}B provides the key metadata about the check --
which paper was checked, and who/when it was checked.  Materials
relating to the codecheck are freely available via the Repository
link.  Figure~\ref{fig:cert}C is a summary of how the codecheck was
performed, and any interesting findings.

Turning to page 2 of the certificate, in Figure~\ref{fig:cert}D we
have a table that is a list of the outputs that were generated from
the codecheck (this is termed the MANIFEST.)  For each output, there
is a comment stating which figure/table it should be compared to in
the original paper, along with the size of the file.  On Page 3,
Figure~\ref{fig:cert}E shows some more detailed notes from the
codechecker, in this case indicating what steps were needed to
initialize the environment and run the code.  This particular example
was quite long, taking about 17 hours to run.  Finally, on page 4 of
the certificate, we see the first output that was generated by the
codecheck (Figure~\ref{fig:cert}F).  In this case, the figure matches
figure 4 of REF.  Subsequent pages of the certificate show other
outputs (not shown here).

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{figs/annotate-cert-crop.pdf}
  \caption{Annotated certificate 2020-012 (first four pages only).}
  \label{fig:cert}
\end{figure}
